Temporal Split

### 2023-01-25 workflow/notebooks/temporal-split.Rmd
Write rule to render Rmd notebooks in exploratory dir

```{r deps}
library(here)
library(mikropml)
library(rlang)
library(tidyverse)
```

@@

```{r perf-95-ci}
perf_dat <- read_csv(here('results','temporal-split','performance_results.csv'))
perf_dat %>% 
  filter(term %in% c('cv_metric_AUC', "AUC")) %>% 
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
  ) %>% 
  rename(estimate = .estimate,
         lower = .lower,
         upper = .upper) %>% 
  ggplot(aes(x = estimate, xmin = lower, xmax = upper, y = outcome, color = term)) +
  geom_pointrange(position = position_dodge(width = 0.1)) +
  schtools::theme_sovacool()
```

>>>>

```{r deps}
library(here)
library(knitr)
library(mikropml)
library(rlang)
library(schtools)
library(tidyverse)
```

@@

```{r temporal-split_perf-95-ci}
perf_dat <- read_csv(here('results','temporal-split','performance_results.csv'))
perf_dat %>% 
  filter(term %in% c('cv_metric_AUC', "AUC")) %>% #, 'prAUC')) %>% 
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
  ) %>% 
  rename(estimate = .estimate,
         lower = .lower,
         upper = .upper) %>% 
  ggplot(aes(x = estimate, xmin = lower, xmax = upper, y = outcome, color = term)) +
  geom_pointrange(position = position_dodge(width = 0.1)) +
  facet_wrap('dataset') +
  theme_sovacool()
```

## Computational resources

```{r temporal-split_bench}
bench_dat <- read_csv(here('results','temporal-split','benchmarks_results.csv'))
bench_dat %>% 
  ggplot(aes(x = s, y = outcome, color = dataset)) +
  geom_point() +
  scale_x_time() +
  theme_sovacool()
```

## Feature importance

```{r temporal-split_feat-imp}
feat_dat <- read_csv(here('results','temporal-split','feature-importance_results.csv'))
tax_dat <- read_tax(here('data','mothur','cdi.taxonomy'))
important_feats <- feat_dat %>% 
  rename(otu = names) %>% 
  left_join(tax_dat, by = 'otu') %>% 
  filter(pvalue < 0.05, perf_metric_diff > 0) %>% 
  arrange(perf_metric_diff)
important_feats %>% 
  mutate(otu = factor(otu, levels = important_feats %>% pull(otu) %>% unique())) %>% 
  ggplot(aes(x = perf_metric_diff, y = label_html, color = outcome, shape = dataset)) +
  geom_point() +
  theme_sovacool() +
  theme(axis.text.y = ggtext::element_markdown())
```
